Output Summary

### 2022-01-25 03-post-process/compare-sim-to-obs.Rmd
Implement improved post-MCMC thinning in Rmds

---
title: "Observed vs. Simulated Year Comparison"
subtitle: "`r paste0('Model Scenario: ', params$scenario)`"
output: html_document
params:
  scenario:
    label: "Scenario"
    value: "base"
    input: text
editor_options: 
  chunk_output_type: console
---

@@

# extract the two key structures from this object
post = model_info$post                               # full posterior takes a long time to run on this script
# post = post_thin(model_info$post, keep_percent = 0.05)  # uncomment this to run document with 5% of the retained MCMC samples
jags_data = model_info$jags_data
```

>>>>

---
title: "Observed vs. Simulated Year Comparison"
subtitle: "`r paste0('Model Scenario: ', params$scenario)`"
date: "`r paste0('Date Rendered: ', Sys.Date())`"
output:
   html_document:
    toc: true
    toc_float: true
params:
  scenario:
    label: "Scenario"
    value: "base"
    input: text
  thin_percent:
    label: "Proportion of Posterior Samples to Retain?"
    value: 1
    input: numeric
editor_options: 
  chunk_output_type: console
---

@@

# extract the posterior samples
# post-MCMC thinning allowed to reduce run time of this document
if (params$thin_percent < 1) {
  post = post_thin(model_info$post, keep_percent = params$thin_percent)
} else {
  post = model_info$post
}

# extract the model data 
jags_data = model_info$jags_data
```

### 2022-01-25 03-post-process/output-plots.Rmd
Implement improved post-MCMC thinning in Rmds

---
title: "Output Summary"
subtitle: "Multi-Population Model"
output: 
  html_document:
    toc: true
    toc_float: true
params:
  scenario:
    label: "Scenario"
    value: "base"
    input: text
  include_sim_years:
    label: "Include Simulated Years on Plots?"
    value: FALSE
    input: checkbox
editor_options: 
  chunk_output_type: console
---

@@

# extract the two key structures from this object
post = model_info$post
# post = post_thin(model_info$post, keep_percent = 0.1)  # uncomment this to run document with 10% of the retained MCMC samples
jags_data = model_info$jags_data
```

>>>>

---
title: "Output Summary"
subtitle: "`r paste0('Model Scenario: ', params$scenario)`" 
date: "`r paste0('Date Rendered: ', Sys.Date())`"
output: 
  html_document:
    toc: true
    toc_float: true
params:
  scenario:
    label: "Scenario"
    value: "base"
    input: text
  include_sim_years:
    label: "Include Simulated Years on Plots?"
    value: TRUE
    input: checkbox
  thin_percent:
    label: "Proportion of Posterior Samples to Retain?"
    value: 1
    input: numeric
editor_options: 
  chunk_output_type: console
---

@@

# extract the posterior samples
# post-MCMC thinning allowed to reduce run time of this document
if (params$thin_percent < 1) {
  post = post_thin(model_info$post, keep_percent = params$thin_percent)
} else {
  post = model_info$post
}

# extract the model data 
jags_data = model_info$jags_data
```
